Supplement B: Stationwise Evaluation

### 2018-10-31 pkg/disttree/inst/draft/supplement/supplement_stationwise.Rnw
typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2367 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0d580b958d1f6ff70bb8f8a5afe8157b8006a68d
changed numbering of supplements (A and B instead of 1 and 2)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2369 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 9093ae989a286d620c85bcfcb92b68ad87d3c504

\title{Supplement 2: Stationwise Evaluation}

@@

\Abstract{
  In the case study presented in the main manuscript ``Distributional Regression
  Forests for Probabilistic Precipitation Forecasting in Complex Terrain''
  the novel distributional regression forests are evaluated and compared with
  other distributional regression approaches on 95 meteorological stations.
  Moreover, further details -- including a cross-validation analysis -- are
  preformed for only one station, Axams. To show that Axams is a fairly typical
  station and similar insights can be obtained for other stations as well,
  this supplements presents the same analysis as in Section~3.3 of the main
  manuscript for 14~further meteorological stations.
}

@@

Based on the out-of-sample CRPS results it can be concluded that the
distributional forest generally performs well on all stations and is typically
close to (e.g., \hyperlink{sumLech.1}{Lech}) or somewhat better than
the (next-)best method (e.g., \hyperlink{sumSeeimPaznaun.1}{See im Paznaun} and
\hyperlink{sumGinzling.1}{Ginzling}). Naturally, there is more variation
in the single-split results with another models performing better than the
distributional forest. However, in the cross-validation such differences
often even out, showing that distributional forests are on par. Examples for
this include \hyperlink{sumRotholz.1}{Rotholz},
\hyperlink{sumMatreiinOsttirol.1}{Matrei in Osttirol}, and 
\hyperlink{sumOchsengartenObergut.1}{Ochsengarten-Obergut}, where the 
best models in the single split are EMOS, prespecified GAMLSS and boosted
GAMLSS, respectively. The only station, where another model performs
clearly better than distributional forests in both settings, is
\hyperlink{sumSt.JohannimWalde.1}{St.~Johann im Walde}.

>>>>

\title{Supplement B: Stationwise Evaluation}

@@

\Abstract{
  In the case study presented in the main manuscript ``Distributional Regression
  Forests for Probabilistic Precipitation Forecasting in Complex Terrain''
  the novel distributional regression forests are evaluated and compared with
  other distributional regression approaches on 95 meteorological stations.
  Moreover, further details -- including a cross-validation analysis -- are
  preformed for only one station, Axams. To show that Axams is a fairly typical
  station and similar insights can be obtained for other stations as well,
  this supplement presents the same analysis as in Section~3.3 of the main
  manuscript for 14~further meteorological stations.
}

@@

Based on the out-of-sample CRPS results it can be concluded that the
distributional forest generally performs well on all stations and is typically
close to (e.g., \hyperlink{sumLech.1}{Lech}) or somewhat better than
the (next-)best method (e.g., \hyperlink{sumSeeimPaznaun.1}{See im Paznaun} and
\hyperlink{sumGinzling.1}{Ginzling}). Naturally, there is more variation
in the single-split results with another model performing better than the
distributional forest. However, in the cross-validation such differences
often even out, showing that distributional forests are on par. Examples for
this include \hyperlink{sumRotholz.1}{Rotholz},
\hyperlink{sumMatreiinOsttirol.1}{Matrei in Osttirol}, and 
\hyperlink{sumOchsengartenObergut.1}{Ochsengarten-Obergut}, where the 
best models in the single split are EMOS, prespecified GAMLSS and boosted
GAMLSS, respectively. The only station, where another model performs
clearly better than distributional forests in both settings, is
\hyperlink{sumSt.JohannimWalde.1}{St.~Johann im Walde}.
